### 2015-07-16 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Modif in coupling w AxiSEM manual

\item[\textbullet] {\color{red} Check the file 'expand\_2D\_3D.par', cf THE PATHS IN THE 3 LAST LINES (normally, these are the only paths you to modify in the AxiSEM dir) !!} ==> Caution : for the tractions path (Tractions/1/), the directory need to be created !! ==>

it is created in the script 'sub\_launch\_script\_for\_make\_+\_run\_expand2D3D\_and\_reformat\_Curie\_CD.sh', but if you don't use this script, you have to create the directory yourself

>>>>

\item[\textbullet] {\color{red} Check the file 'expand\_2D\_3D.par', cf THE PATHS IN THE 3 LAST LINES (normally, these are the only paths you to modify in the AxiSEM dir) !!} ==> Caution : for the tractions path (for example: /[...]/AxiSEM\_tractions/1/), the directory need to be created !!!! {\color{red} ~ ==>}

the script 'sub\_launch\_script\_for\_make\_+\_run\_expand2D3D\_and\_reformat\_Curie\_CD.sh' create a traction directory here:

{\footnotesize 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation/DATA/AxiSEM\_tractions/1/', }

BUT, if you don't use this script or if you want to create another tractions dir, you have to create the directory yourself.
